Non-kissing and non-crossing complexes \\ for locally gentle algebras

### 2018-07-03 draft/accordionComplexSurfaces.tex

This construction is illustrated on \fref{fig:examplesSurfaces}.
%
\begin{figure}[t]
	\capstart
	\centerline{\includegraphics[scale=.7]{examplesSurfaces}}
	\caption{The surface~$\surface_{\bar Q}$ for two quivers~$\bar Q$ of \fref{fig:quivers}.}
	\label{fig:examplesSurfaces}
\end{figure}
%
Definition~\ref{def:surfaceQuiver} constructs an orientable surface~$\surface(\bar Q)$ with boundaries.
Note that we could equivalently construct the surface~$\surface_{\bar Q}$ as follows:
\begin{itemize}
\item 
\item
\end{itemize}
\vincent{TODO}
The advantage of Definition~\ref{def:surfaceQuiver} is that it automatically endows with two disjoint sets~$V_{\bar Q}$ and~${V_{\bar Q}}\dual$ of marked points and two dual dissections~$\dissection_{\bar Q}$ and~${\dissection_{\bar Q}}\dual$ defined as follows.

@@

\begin{remark}
Observe that
\begin{itemize}
\item $V_{\bar Q}$ has one vertex for each straight walk in~$\bar Q$.
\item $\dissection_{\bar Q}$ has one arc for each vertex~$p \in \bar Q_0$, obtained by concataining the sides~$\Enrt{\alpha} = \Enrs{\beta}$ and~$\Enrt{\alpha'} = \Enrs{\beta'}$ where~$p = t(\alpha) = s(\beta) = t(\alpha') = s(\beta')$, $\alpha\beta \notin I$ and~$\alpha'\beta' \notin I$.
\item 
\end{itemize}
\vincent{TODO}
A similar remark holds dually for~${V_{\bar Q}}\dual$ and~${\dissection_{\bar Q}}\dual$.
Finally, observe that we could also have constructed the surface
\end{remark}

>>>>

This construction is illustrated on \fref{fig:examplesSurfaces}.
%
\begin{figure}[t]
	\capstart
	\centerline{\includegraphics[scale=.7]{examplesSurfaces}}
	\caption{The surface~$\surface_{\bar Q}$ for the first four quivers~$\bar Q$ of \fref{fig:quivers}. The boundaries of the surfaces are shaded (the second surface has no boundary, it is just a sphere).}
	\label{fig:examplesSurfaces}
\end{figure}
%
Definition~\ref{def:surfaceQuiver} constructs an orientable surface~$\surface(\bar Q)$ with boundaries.
Note that we could equivalently construct the surface~$\surface_{\bar Q}$ as follows:
\begin{itemize}
\item consider one $(\ell+1)$-gon~$P_\omega$ for each straight walk~$\omega$ of length~$\ell$ in~$\bar Q$ or in~$\bar Q\koszul$ (just closing~$\omega$ with an additional edge connecting~$t(\omega)$ to~$s(\omega)$),
\item for each arrow~$\alpha \in Q_1\blossom$, consider the only straight walks~$\omega$ of~$\bar Q$ and~$\omega\koszul$ of~$\bar Q\koszul$ containing~$\alpha$, and glue the polygons~$P_\omega$ and~$P_{\omega\koszul}$ along their edges corresponding to~$\alpha$.
\end{itemize}
The advantage of Definition~\ref{def:surfaceQuiver} is that it automatically endows with two disjoint sets~$V_{\bar Q}$ and~${V_{\bar Q}}\dual$ of marked points and two dual dissections~$\dissection_{\bar Q}$ and~${\dissection_{\bar Q}}\dual$ defined as follows.

@@

\begin{remark}
Observe that
\begin{itemize}
\item $V_{\bar Q}$ has one vertex for each straight walk in~$\bar Q$.
\item $\dissection_{\bar Q}$ has one arc for each vertex~$p \in \bar Q_0$, obtained by concataining the sides~$\Enrt{\alpha} = \Enrs{\beta}$ and~$\Enrt{\alpha'} = \Enrs{\beta'}$ where~$p = t(\alpha) = s(\beta) = t(\alpha') = s(\beta')$, $\alpha\beta \notin I$ and~$\alpha'\beta' \notin I$.
\item $\dissection_{\bar Q}$ has one $\ell$-cell for each straight walk of length~$\ell$ in~$\bar Q\koszul$.
\end{itemize}
A similar remark holds dually for~${V_{\bar Q}}\dual$ and~${\dissection_{\bar Q}}\dual$.
\end{remark}
